---
title: "Untitled"
description: |
  A new article created using the Distill format.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

OK maybe simpler option, just take screenshots using RSelenium:
https://cran.r-project.org/web/packages/RSelenium/RSelenium.pdf 

https://medium.com/analytics-vidhya/web-scraping-instagram-with-selenium-b6b1f27b885

```{r}
library(RSelenium)
```

omg wait instaloader is workingggg

------


Using the pre-made Python modules failed miserably. So now I am looking into whether or not you can automate Chrome devtools:
https://rahulshettyacademy.com/blog/index.php/2021/11/04/selenium-4-feature-chrome-dev-tools-protocol/ 

- The Chrome Dev Tools is an API that provides features to perform operations on dev tools programmatically by calling those API methods.

- Selenium 4 commands
send()
executeCDPCommand()


Documentation:
https://chromedevtools.github.io/devtools-protocol/ 

Get a DOM snapshot:
https://chromedevtools.github.io/devtools-protocol/tot/DOMSnapshot/#method-captureSnapshot

Work with the DOM:
https://chromedevtools.github.io/devtools-protocol/tot/DOM/



load library

```{r}
library(instaloadeR)
library(reticulate)
```

install necessary python

```{r}
install_instaloadeR()
```

initialize

```{r}
init_instaloadeR()
```

get coronovairus posts

```{r}

corona <- insta_posts(query = "coronavirus", 
                         scope = "hashtag",
                         max_posts = 10, 
                         scrape_comments = F)


corona
```

get from a user

```{r}

francediplo <- insta_posts(query = "francediplo", 
                         scope = "username",
                         max_posts = 10, 
                         scrape_comments = F)


francediplo
```

try in bash

```{python}
# Get instance
import instaloader

L = instaloader.Instaloader()

# Login or load session
username = "academic_joshua"
password = "s6PQOT77N3"
L.login(username, password)  # (login)
```

```{python}
for post in instaloader.Hashtag.from_name(L.context, 'fireislandpines').get_posts():
    # post is an instance of instaloader.Post
    L.download_post(post, target='#fireislandpines')

```

```{python}
for post in instaloader.Hashtag.from_name(L.context, 'kohenet').get_posts():
    # post is an instance of instaloader.Post
    L.download_post(post, target='#kohenet')
    
```


